Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)

### 2019-12-23 3-UHD/report/paper.tex
Replace en-dash with its ASCII equivalent
Otherwise pdfLaTeX will report errors for these characters.
Add an introduction for Project 3' report

\section{Introduction}
\IEEEPARstart{U}tral-High Definition images refer to images with extremely high definitions.
A common UHD is 4K resolution, which includes many definitions, one of which is 3840*2160 and is the images under the consideration of this project.

@@

\subsubsection{Bilinear Interpolation}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to −0.5 or −0.75.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

>>>>

\section{Introduction}
\IEEEPARstart{U}tral-High Definition images refer to images with extremely high definitions.
A common UHD is 4K resolution, which includes many definitions, one of which is 3840*2160 and is the images under the consideration of this project. 4K content, due to its high resolution and preservation of fine details, is superior in image quality to 2K and traditional HD content, and thus significantly enhance visual experience. 4K content, especially 4K videos, is prevalent on all mainstream content providers. Also, given content providers' unprecedented willingness to purchase 4K content even at a much higher price, it is only natural that customers' acceptance and desire for 4K content will continue to increase.

But the upgrade from HD to 4K is not only a change in the number of pixels. A complete upgrade of existing equipment and more processing power are only some of the prerequisites for producing true 4K videos. Customers' (and therefore content providers') desire for 4K content and the high cost of 4K production have given rise to a new concerning trend: some producers are actively selling 4K videos upscaled from 2K or HD to content providers, at the same price as true 4K videos. Wenhan \textit{et al.} \cite{zhu2016distinguish} claimed that visual quality of fake 4K videos are often worse than the HD contents being upscaled automatically by the 4K display devices due to the fact that their compression rate is generally higher to meet the bandwidth constraint. A method for distinguishing fake 4K from true 4K content has wide applications in real-life scenarios.

Distinguishing fake 4K videos by subjective assessment is difficult and inefficient, because their differences in spatial domain are small. Also, the recent advancement of deep neural networks (DNN) for super resolution calls for evaluation of existing methods and possibly new methods. DNNs for super resolution are fundamentally different from traditional upscaling methods and capable of generating convincing high-resolution images from low-resolution images because of their strong priors.

In this paper, we devise several methods to distinguish between true and fake 4K images. A dataset of fake 4K images is generated by first downsampling and then upscaling true 4K images, with both traditional methods like bilinear, bicubic, Lanczos and DNNs like SRCNN \cite{dong2015image} and EDSR \cite{lim2017enhanced}. The final SVM classifier achieves an accuracy rate greater than 95\% on the test set.

@@

\subsubsection{Bilinear Interpolation}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to $-0.5$ or $-0.75$.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:
